Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-05-30 PaperLatex/paper.tex
Set up simulations in NEURON
Restructure text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		WORKED EXAMPLES
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Worked Examples}
\label{sec:examples}

@@

@@

\subsection{Modeling}

\subsubsection{Using the \texttt{cpplab} Framework}

\begin{lstlisting}[style=Matlab-editor]
	x.set(x.find('HH*gbar'), gbars)
\end{lstlisting}

\subsubsection{Compartments and Synapses}

\subsubsection{Conductances and Controllers}

\subsubsection{Creating Custom \texttt{cpplab} Objects}

\subsection{Simulation}

\subsection{Using the graphical interface to manipulate parameters}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		DESIGN GOALS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Design Goals}
\label{design}

"xolotl" is designed to be easy-to-use without sacrificing speed. The software has been designed in "MATLAB" due to its popularity among neuroscientists for pedagogy and research. "xolotl" capitalizes on "MATLAB"'s straightforward structure array syntax to permit rapid prototyping and experimentation, especially for small neuronal networks of complex models. Parameters of conductances, neuronal compartments, and simulations may all be edited in the structure before any calls to integration functions. The underlying code is written in "C++" for speed and memory optimization, and while models can indeed be integrated using the compiled binary, symbolic manipulations can be readily performed in "MATLAB" without ever touching the foundational code.

\subsection{Features}
\label{features}

\paragraph{Using the \texttt{cpplab} framework.}

\begin{lstlisting}[style=Matlab-editor]
x.set('HH*gbar', gbars)
\end{lstlisting}

\paragraph{Compartments and synapses.}

\paragraph{Conductances and controllers.}

\paragraph{Creating custom \texttt{cpplab} objects.}

\paragraph{Simulation.}

\paragraph{Using the graphical interface to manipulate parameters.}

\paragraph{Optimizing parameters.}
"xolotl" can use the Global Optimization and Parallel Computing toolboxes for "MATLAB" to optimize network parameters.

\subsection{Limitations}
\label{limitations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		USAGE EXAMPLES
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Usage Examples}
\label{usage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		BENCHMARKS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Benchmarks}
\label{benchmarks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		DISCUSSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{discussion}

\subsection{Reproducibility}

\subsection{Circumventing Language Tradeoffs}

\subsection{Applications of \texttt{cpplab}}

@@
